Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-06 paper.tex
Fix confusion between submanifolds and manifols.

\textbf{This section presents an algorithm for constrained motion
  planning in the configuration space $\mathcal{C}$. In the particular
  case of a humanoid robot which is an under-actuated system,
  $\mathcal{C}=\mathcal{Q} \times SE(3)$, where $\mathcal{Q}$
  represents the kinematic tree actuators and $SE(3)$ corresponds to a
  fictitious floating joint attached to the root of the tree. If the
  robot has $n$ actuated DoFs, then $dim(\mathcal{Q})=n$ and
  $dim(\mathcal{C})=n+6$. A configuration $q$ of $\mathcal{C}$ is said
  to be valid iff, besides being collision-free, it lies on a specific
  submanifold $\manifold$ of $\mathcal{C}$. $\manifold$ is called
  the planning submanifold.}

The problem solved here differs from classic approaches in two ways:
\begin{enumerate}
\item the set of valid configurations is defined implicitly, as the
  set of collision-free configurations satisfying a given set of
  inverse kinematics balance constraints;
\item the goal submanifold $\goalmanifold$ is also defined implicitly,
  by additional inverse kinematics constraints.
\end{enumerate}
\textbf{During global planning, we will consider several types of
equality constraints for various reasons:}
\begin{itemize}
\item Static balance: the CoM of the robot stays above
  the support polygon center, the two feet have fixed position and
  orientation.
\item End-effector position and orientation: the goals of some problems presented
  in the experimental section of this paper are defined as a specific robot hand pose,
  or a gaze direction.
\item Configuration task: our adaptation of randomized motion planning algorithms 
  uses tasks defined as the distance towards a given configuration in $\mathcal{C}$. 
  This will be detailed in the following section.
\end{itemize}

@@

One way to make the RRT algorithm more efficient is to grow trees from both the initial
and  goal configurations. This was first proposed in 
\cite{kuffner00rrtconnect}. Our formulation of manipulation planning does
not include an explicit goal configuration, so it is not possible to directly grow
a tree from the goal. To make use of the idea of growing multiple trees, we first
randomly sample the goal submanifold and generate several goal configurations. Then, 
we grow random
trees from the initial configuration and the random goal configurations. The idea of
generating several goals for manipulation planning was proposed in \cite{diankov2008bpc}.

>>>>

\textbf{This section presents an algorithm for constrained motion
  planning in the configuration space $\mathcal{C}$. In the particular
  case of a humanoid robot which is an under-actuated system,
  $\mathcal{C}=\mathcal{Q} \times SE(3)$, where $\mathcal{Q}$
  represents the kinematic tree actuators and $SE(3)$ corresponds to a
  fictitious floating joint attached to the root of the tree. If the
  robot has $n$ actuated DoFs, then $dim(\mathcal{Q})=n$ and
  $dim(\mathcal{C})=n+6$. A configuration $q$ of $\mathcal{C}$ is said
  to be valid iff, besides being collision-free, it lies on a specific
  submanifold $\manifold$ of $\mathcal{C}$. $\manifold$ is called
  the planning manifold.}

The problem solved here differs from classic approaches in two ways:
\begin{enumerate}
\item the set of valid configurations is defined implicitly, as the
  set of collision-free configurations satisfying a given set of
  inverse kinematics balance constraints;
\item the goal manifold $\goalmanifold$ is also defined implicitly,
  by additional inverse kinematics constraints.
\end{enumerate}
\textbf{During global planning, we will consider several types of
equality constraints for various reasons:}
\begin{itemize}
\item Static balance: the CoM of the robot stays above
  the support polygon center, the two feet have fixed position and
  orientation.
\item End-effector position and orientation: the goals of some problems presented
  in the experimental section of this paper are defined as a specific robot hand pose,
  or a gaze direction.
\item Configuration task: our adaptation of randomized motion planning algorithms 
  uses tasks defined as the distance towards a given configuration in $\mathcal{C}$. 
  This will be detailed in the following section.
\end{itemize}

@@

One way to make the RRT algorithm more efficient is to grow trees from both the initial
and  goal configurations. This was first proposed in 
\cite{kuffner00rrtconnect}. Our formulation of manipulation planning does
not include an explicit goal configuration, so it is not possible to directly grow
a tree from the goal. To make use of the idea of growing multiple trees, we first
randomly sample the goal manifold and generate several goal configurations. Then, 
we grow random
trees from the initial configuration and the random goal configurations. The idea of
generating several goals for manipulation planning was proposed in \cite{diankov2008bpc}.
